A new tidy data structure to support exploration and modeling of temporal data

### 2019-01-28 main.Rmd
Section 2.3

Current standards, provided by the native `ts` object in R, extended by **zoo** [@zoo2005], and **xts** [@R-xts], assemble temporal data into matrices with implicit time indexes. These objects were designed for modelling methods. The diagram in the style of \autoref{fig:tsibble-fit}, would place the model at the center of the analytical universe, and all the transformations and visualisations would hinge on that format. This is contrary to the tidyverse conceptualisation, which holistically captures the full data workflow.

>>>>

Current standards, provided by the native `ts` object in R, and extended by **zoo** [@zoo2005] and **xts** [@R-xts], assemble temporal data into matrices with implicit time indexes. These objects were designed for modeling methods. The diagram in the style of \autoref{fig:tsibble-fit} would place the model at the center of the analytical universe, and all the transformations and visualizations would hinge on that format. This is contrary to the tidyverse conceptualization, which holistically captures the full data workflow.
